|

### 2022-05-25 text/SupportManuscriptDraft.Rmd
Updated filtering results in supporting info

**Table S1:** Results of the filtering algorithm for filtering distances 5-500 with a stepsize of 50 for all three series.

![](../figures/FullFilteringDistanceTest.png){ width=100% }

>>>>

## Results of the filtering algorithm for filtering distances 5-500 with a stepsize of 50 for the three series.

eps = 50: 158 mismatches with 165 tracks kept 
eps = 100: 103 mismatches with 147 tracks kept 
eps = 150: 71 mismatches with 124 tracks kept 
eps = 200: 47 mismatches with 100 tracks kept 
eps = 250: 30 mismatches with 69 tracks kept 
eps = 300: 9 mismatches with 49 tracks kept 
eps = 350: 0 mismatches with 28 tracks kept 
eps = 400: 0 mismatches with 18 tracks kept 
eps = 450: 0 mismatches with 16 tracks kept 
eps = 500: 0 mismatches with 11 tracks kept

#![](../figures/FullFilteringDistanceTest.png){width="100%"}
